P3064R2: How to Avoid OOTA Without Really Trying

### 2024-07-12 ootavacuous.tex
Update paper number and add a history appendix
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

\begin{document}
\title{P3064R1: How to Avoid OOTA Without Really Trying}

@@

\author{
Alan Stern\\{\small \email{stern@rowland.harvard.edu}} \and
Paul E.~McKenney\\{\small \email{paulmck@kernel.org}} \and
Michael Wong\\{\small \email{fraggamuffin@gmail.com}} \and
Maged Michael\\{\small \email{maged.michael@gmail.com}}
}
\date{May 4, 2024 (Pre-St. Louis)}
\maketitle{}

@@

% \section{History}
% \label{sec:History}

@@

% Done as of December 18, 2023 %% as of March 18, 2023
%% David Goldblatt
%% Boqun Feng, Uladzislau Rezki, Neeraj Upadhyay, Joel Fernandes, and
%	Frederic Weisbecker (RCU proteges)
%% Michael Wong
%% Maged Michael
% John Wickerson: Thank you.  OK for Peter Sewell, Mark Batty, etc.
%% Akira Yokosawa: Professional courtesy, perfbook memory models.
%% Dan Kelley, Alexei Starovoitov, Mykola Lysenko: FYI.  OOTA dropped
% Alan Jeffrey: Fixed-point insight P0422R0.  Reached out via LinkedIn.
%% Jade Alglave: C++ herd model?  Memory models and variety of hardware.
%% Alan Stern: Memory models, mathematical logic, and variety of hardware.
% Martin Uecker (offered)
% Peter Sewell
% Mark Batty
% Richard Gristenthwaite: ARM hardware.  Posed HW speculation question.
% Peter Zijlstra.
% Mark Rutland: ARM memory ordering.
% Will Deacon: ARM hardware, C++, and OOTA.
%% Greg Kroah-Hartman and Linus Torvalds: FYI, trouble being caused.
%% Olivier Giroux: Skeptic, memory models, NVIDIA, requested.
%% Gonzalo Brito <gonzalob@nvidia.com>

@@

>>>>

\begin{document}
\title{P3064R2: How to Avoid OOTA Without Really Trying}

@@

\author{
Alan Stern\\{\small \email{stern@rowland.harvard.edu}} \and
Paul E.~McKenney\\{\small \email{paulmck@kernel.org}} \and
Michael Wong\\{\small \email{fraggamuffin@gmail.com}} \and
Maged Michael\\{\small \email{maged.michael@gmail.com}}
}
\date{July 12, 2024 (Post-St. Louis)}
\maketitle{}

@@

@@

% Done as of December 18, 2023 %% as of March 18, 2024
%% David Goldblatt
%% Boqun Feng, Uladzislau Rezki, Neeraj Upadhyay, Joel Fernandes, and
%	Frederic Weisbecker (RCU proteges)
%% Michael Wong
%% Maged Michael
% John Wickerson: Thank you.  OK for Peter Sewell, Mark Batty, etc.
%% Akira Yokosawa: Professional courtesy, perfbook memory models.
%% Dan Kelley, Alexei Starovoitov, Mykola Lysenko: FYI.  OOTA dropped
% Alan Jeffrey: Fixed-point insight P0422R0.  Reached out via LinkedIn.
%% Jade Alglave: C++ herd model?  Memory models and variety of hardware.
%% Alan Stern: Memory models, mathematical logic, and variety of hardware.
% Martin Uecker (offered)
% Peter Sewell
% Mark Batty
% Richard Gristenthwaite: ARM hardware.  Posed HW speculation question.
% Peter Zijlstra.
% Mark Rutland: ARM memory ordering.
% Will Deacon: ARM hardware, C++, and OOTA.
%% Greg Kroah-Hartman and Linus Torvalds: FYI, trouble being caused.
%% Olivier Giroux: Skeptic, memory models, NVIDIA, requested.
%% Gonzalo Brito <gonzalob@nvidia.com>

@@

\section{History}
\label{sec:History}

P3064R2 incorporates feedback from the St.~Louis meeting, primarily
incorporating clear statements that nothing need change to avoid OOTA.
In other words, the title really means what it says.

P3064R1 adds non-OOTA examples that show that inventing, duplicating,
or repurposing atomic loads can violate basic laws of arithmetic.
